### 2021-02-02 about/vita.tex
Added more reports
Tonogenesis

@@

\pubbegin R
\repitem Typechecking proof scripts: making interactive proof assistants robust.
Honours project report, McGill University (Montr\'eal, Qu\'ebec, December 2019), 10 pp.

@@

\parindent=10pt
\thing Scored 10/120 on the William Lowell Putnam Mathematical Competition in 2019
(the median score that year was 2/120).
\smallskip
\thing Recipient of 0x\$3.40 in Knuth reward cheques.
\smallskip
\thing Contributed sequences A335562, A338550, and A338993 to the On-line Encyclopedia of Integer Sequences.
\medbreak

>>>>

\goodbreak

@@

\pubbegin R
\repitem The OPythn programming language. Software project report, Charles University (Prague,
Czech Republic, June 2019), 10 pp.
\repitem Typechecking proof scripts: making interactive proof assistants robust.
Honours project report, McGill University (Montr\'eal, Qu\'ebec, December 2019), 10 pp.
\repitem Grid-building algorithms on manifolds. Summer research report, McGill University (Montr\'eal, Qu\'ebec,
August 2020), 10 pp.

@@

\parindent=10pt
\thing Scored 10/120 on the William Lowell Putnam Mathematical Competition in 2019
(the median score that year was 2/120).
\smallskip
\thing Recipient of 0x\$3.40 in Knuth reward cheques.
\smallskip
\thing Contributed sequences A335562, A338550, A338993, A339941, and A339942
to the On-line Encyclopedia of Integer Sequences.
\medbreak
